Hydras \& Co.

### 2023-09-13 doc/schutte-chapter.tex
fix a few Hint locality attributes
Document the use of zorns-lemma

We use Florian Hatat's library on countable sets, written as he was a student of  \emph{\'Ecole Normale Supérieure de Lyon}. A set $A$ is countable if there is an injective function from $A$ to $\mathbb{N}$ (see 
Library \href{../theories/html/hydras.Schutte.Countable.html}%
{\texttt{Schutte.Countable}}).

>>>>

Countable sets were

 A set $A$ is countable if there is an injective function from $A$ to $\mathbb{N}$ (see 
Library \href{../theories/html/hydras.Schutte.Countable.html}%
{\texttt{Schutte.Countable}}).

This library was initially written by Florian Hatat, as he was a student of  \emph{\'Ecole Normale Supérieure de Lyon}.
St\'ephane Desarzens adapted it in order to make it compatible with
the \texttt{Topology/ZornsLemma} project~\cite{zornslemma}.
